Supporting Information for Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-10-08 si.tex
Almost ready.
Need to read it one more time

In this section, we discuss the evaluation of Herzberg-Teller integrals when the ground and first excited state are harmonic wells of identical curvature.\cite{HerzbergTeller1933}
% We note that Myers et al. have developed a general expression to evaluate Franck-Condon factors for two displaced harmonic wells of differing curvature,\cite{Myers1982} 
We investigate the one dimensional case using the Hamiltonian described in the main text, $H = H_g |g) \left(g| + H_e |e\right) (e|$, where
\begin{subequations}\label{Hamiltonian}
	\begin{equation}
		H_g = \frac{\hbar \omega }{2} \left(p^2 + q^2 \right)
	\end{equation}
	and
	\begin{equation}
		H_e = \frac{\hbar \omega }{2} \left(p^2 +  (q-\Delta)^2 \right) + \hbar \omega_{eg}.
	\end{equation} 
\end{subequations}
Here, $p,q$ are the dimensionless conjugate normal mode coordinates, $\hbar\omega_{eg}$ is the energy difference between $H_e$ and $H_g$, and $\Delta$ is the dimensionless offset of the excited state surface relative to the ground state.
The Hamiltonians are quantum harmonic oscillators.
The solutions to the harmonic oscillator Hamiltonian are well known, and their position space wavefunctions are
\begin{equation}
	\psi_m(q) = \langle q | m \rangle = N_m H_m(q) \exp(-q^2/2),
\end{equation}
where $N_m = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the $m^{th}$ Hermite Polynomial.\cite{RN230, MorseFeshbach}

For an $n$-quantum excited state vibration $| \tilde{n} \rangle$, and a $m$-quantum ground state vibration $\ket{m}$, the $k^{th}$-order vibrational coupling term is
\begin{equation}
	\begin{split}
		\mel{\tilde{n}}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \ \psi^*_n(q-\Delta) q^k \psi_m(q)\\
		&= \int_{-\infty}^\infty \mathrm{d}q \ N_n H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k N_m H_m(q) \exp(-\frac{q^2}{2}). \\
		&= N_n N_m \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ H_n(q-\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
	\end{split}\label{key}
\end{equation}
The integral corresponds to Franck-Condon factors for $k=0$ and Herzberg-Teller integrals for $k=1$.
The vibrational coupling integrals are written assuming the expansion of the dipole moment is taken about the equilibirum point of the ground state geometry ($q=0$), as is done in the main text.
Note that in the limit $\Delta \rightarrow 0$, typical harmonic oscillator selection rules are restored, as the two wells have the same vibrational Hamiltonian and thus share a subspace of orthonormal eigenstates.

\subsection{General Solution to $\langle \tilde{n} | q^k | m \rangle$}
The matrix elements of \autoref{key} can be computed numerically, but analytic forms of the integral also exist. 
Due to the polynomial nature of $H_v(q)$, the product $H_n(q-\Delta) q^k H_m(q)$ will also be a polynomial, so that the integral of equation \autoref{key} will be of the form
\begin{eqnarray}
	\int_{-\infty}^\infty \mathrm{d}q \ P_{nmk}(q) \exp(-q^2 + q\Delta), \\
	P_{nmk}(q) \equiv \sum_\lambda^{n+m+k} a_\lambda q^\lambda
\end{eqnarray}
for some set coefficients $a_\lambda$, to be specified later. We can recast the integral into the linear combination of integrals,
\begin{equation}\label{eq:analytic_form}
	\mel{\tilde{n}}{q^k}{m} = N_n N_m \exp(-\frac{\Delta^2}{2}) \sum_\lambda a_\lambda F_\lambda(\Delta),
\end{equation}
where
\begin{equation}\label{integral}
	F_w(\Delta) \equiv \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta).
\end{equation}
\autoref{integral} can be readily evaluated, as we now show.  When $w=0$, the integral is evaluated by completing the square:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
\begin{equation}
	\begin{split}
		F_0(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 - q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
		&= \exp(\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
	\end{split}
\end{equation}
For the general solution, \autoref{integral} is evaluated via repeated use of a well-known Gaussian identity
\begin{equation}\label{identity}
	\begin{split}
		F_w(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta) = \partial_{\Delta} \int_{-\infty}^\infty \mathrm{d}q \ q^{w-1} \exp(-q^2 + q\Delta) \\
		&= \frac{\mathrm{d}}{\mathrm{d}\Delta} F_{w-1}(\Delta)
	\end{split}
\end{equation}
so we can write\footnote{Setting $-x^2 \ = \ \Delta^2/4$ (so that $x \ = \ i \Delta /2$) and using the chain rule ($\frac{\mathrm{d}}{\mathrm{d}x} =  \frac{\mathrm{d}}{\mathrm{d}\Delta}  \frac{\mathrm{d\Delta}}{\mathrm{d}x}$) provides the final result in \autoref{eq:F_solved}.}
\begin{equation}\label{eq:F_solved}
	\begin{split}
		F_w(\Delta) &= \frac{\mathrm{d}^w}{\mathrm{d}\Delta^w} F_0(\Delta) \\
		&= \sqrt{\pi} \frac{\mathrm{d}^w}{\mathrm{d}\Delta^w} \exp(\frac{\Delta^2}{4}) \\
		&= \sqrt{\pi} \left( -\frac{i}{2} \right)^w \exp(\frac{\Delta^2}{4}) H_w\left(i\frac{\Delta}{2}\right).
	\end{split}
\end{equation}
In the last line we have used the generator definition of Hermite polynomials:  $H_n(x) \equiv (-1)^n e^{x^2} \frac{\mathrm{d}^n}{\mathrm{d}x^n} e^{-x^2}$.\cite{MorseFeshbach}

@@

It is clear from \autoref{fig:fcht_product} that the HDFG spectrum will have a significant dependence upon $\Delta$, even for small deviations from complete overlap. 
To this end, we plot the impact of resonance frequency and offset on the HDFG spectrum \autoref{fig:chgdelta}, using values reported by Myers et al. and Brennan et al. \cite{Myers1982, Brennan2024}
In this section, we take $\omega_{eg}$ = $30000$ cm$^{-1}$ and vary the offset ($\Delta$), vibrational frequency ($\omega_{g1,g0}$), and linewidth ($\Gamma$) as noted in the figure.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/changedelta.png}
	\caption{The impact of offset, vibrational resonance, and linewidth on HDFG spectra. Parameters for (a,b) follow from Myers et al., whereas parameters for (c,d) follow from Brennan et al.\cite{Myers1982, Brennan2024}
	Note that in these plots, the ratio $\abs{A/B} = 0.1$ is enforced.} 
	\label{fig:chgdelta}
\end{figure}

In addition to the linewidth and offset impacting the shape of the HDFG response, the sign of the molecular parameters $M^{ge}_0, \Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q}$ will significantly impact the HDFG spectrum.
As discussed in the main text, the atypical lineshape in the post-resonance region of the HDFG region arises due to the sign of all four aforementioned parameters being identical.
Changing the sign of one (or three) parameters will change the sign of $A, B$ and eliminate interference between the real and imaginary terms.  
As an example, we demonstrate the resultant HDFG spectrum when $M_0^{ge} < 0$, and all other terms $>0$ (\autoref{fig:chgsign}).
Compared to Figure 3 of the main text, the contributions from the $A, B_1$ and $B_2$ terms to $\Re(\gamma)$ and $\Im(\gamma)$ significantly change.
In particular, $\Re(\gamma)$ and $\Im(\gamma)$ are of similar value in the post-resonance region, eliminating the interference seen in Figure 3 of the main text.
\newpage
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/drsive_chgsign.png}
	\caption{Contributions of $A, B$ to HDFG spectrum for a simple two harmonic well system, identical to the main text, except $M_0^{ge} < 0$.
		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c, d) real and imaginary parts of terms plotted in (b), respectively.
		The spectra are referenced to $\max{(A+B)}$. 
		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
} 
	\label{fig:chgsign}
\end{figure}
\pagebreak
\section{Evaluating impact of static inhomogeneity on HDFG output}
In this section, the integral
\begin{equation}\label{generalcontour}
	\begin{split}
		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
		&= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)} \\
		&= \frac{\eta_{ijkl} \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + c\xi}\\
	\end{split}
\end{equation}
is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) and $c=1$ (electronic state and vibrational state energy fluctuations are correlated).

Integrals such as \autoref{generalcontour} can be evaluated by using the Residue theorem.\cite{MorseFeshbach}
For clarity, we briefly outline the technique.
%@dan i had too much white space, needed something to fill in... delete if you want.
Consider the integral
\begin{equation}
	\int_{-\infty}^{\infty} \mathrm{d}x f(x)
\end{equation}
If $\int_{-\infty}^{\infty} \mathrm{d}x f(x)$ exists %is this strict enough?
and $f(z)$ is an analytic function, where $z$ is a complex variable, then
\begin{subequations}\label{eq:generalcontour}
	\begin{equation}
		\int_{-\infty}^{\infty}  \mathrm{d}x f(x) = 2\pi i \sum_k \Res[f(z_k)]
	\end{equation}
where $\Res[f(z_k)]$ refers to the residue of $f(z)$ in the upper half of the complex plane at the pole $z_k$ and the sum is taken over all the poles, i.e., non-removable singularities, of $f(z)$.
Note that the residue of an n$^{\text{th}}$ order pole at $z = z_k$ is evaluated as
	\begin{equation}
		\Res[f(z_k)] = \lim_{z \rightarrow z_k} \frac{1}{\left(n-1\right)!} \frac{\mathrm{d}^{n-1}}{\mathrm{d}z^{n-1}} \left[f(z) (z-z_k)^n \right]
	\end{equation}
For first order poles (the cases considered below), $n=1$, so that 
	\begin{equation}
		\int_{-\infty}^{\infty} \mathrm{d}x f(x) = 2\pi i \sum_k \lim_{z \rightarrow z_k} f(z) (z-z_k)
	\end{equation}
\end{subequations}
Note that in \autoref{eq:generalcontour}, the integrals are closed along a contour which wraps all the poles in the positive half of the complex plane.

\subsection{Anti-correlated Modes}
For anti-correlated modes ($c = -1$), the poles ($\xi_k$) are situated in the complex plane as shown in \autoref{fig:contours}a.
For c = -1, there are four poles: $\pm i \sigma, \Delta_{ga}, \Delta_{ba}$. 
The contour that wraps the upper half of the complex plane has only one pole, $i \sigma$
Using the residue theorem for a first order pole,\cite{Carlson1990line} we see
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi} (\xi - i \sigma)\\
			&= 2 \eta_{ijkl} \sigma i \lim_{\xi \rightarrow i\sigma} \frac{1}{\xi + i\sigma} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi}\\
			&= 2\eta_{ijkl} \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} - i\sigma}\\
			&= \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma\right)\left(\Delta_{ba}-i \sigma\right)}\\
		\end{split}
	\end{equation}
\end{widetext}

\subsection{Correlated Modes}
For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
We evaluate along the contour where the poles are $\{i\sigma, -\Delta_{ba}\}$.
Since the $\xi_k$ are nondegenerate,
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi}  \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + \xi} \left(\xi - i \sigma\right) \\ 
			&+ 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow -\Delta_{ba}} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + \xi} \left(\xi + \Delta_{ba}\right)\\
			&= 2 \eta_{ijkl} i \sigma \left(\frac{1}{2 i \sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} + i\sigma} \right) + 2\eta_{ijkl} i \sigma \left(\frac{1}{\sigma^2 + \Delta_{ba} ^2} \frac{1}{\Delta_{ga} + \Delta_{ba}} \right)\\
			&= \frac{\eta_{ijkl}}{\Delta_{ba} + i \sigma} \left(\frac{1}{\Delta_{ga} - i \sigma} + \frac{2i\sigma}{(\Delta_{ba} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right)\\
		\end{split}
	\end{equation}
\end{widetext}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/corr_contour.png}
	\caption{Poles (blue dots) and contours (black lines) used to evaluate \autoref{generalcontour} for (a) anti-correlated ($c=-1$) and (b) correlated ($c=1$) modes. 
	} 
	\label{fig:contours}
\end{figure}

>>>>

In this section, we discuss the evaluation of Herzberg-Teller integrals when the ground and first excited state are harmonic wells of identical curvature.\cite{HerzbergTeller1933}
% We note that Myers et al. have developed a general expression to evaluate Franck-Condon factors for two displaced harmonic wells of differing curvature,\cite{Myers1982} 
We investigate the one dimensional case using the Hamiltonian described in the main text, $H = H_g |g) \left(g| + H_e |e\right) (e|$, where
\begin{subequations}\label{Hamiltonian}
	\begin{equation}
		H_g = \frac{\hbar \omega }{2} \left(p^2 + q^2 \right)
	\end{equation}
	and
	\begin{equation}
		H_e = \frac{\hbar \omega }{2} \left(p^2 +  (q-\Delta)^2 \right) + \hbar \omega_{eg}.
	\end{equation} 
\end{subequations}
Here, $p,q$ are the dimensionless conjugate normal mode coordinates, $\hbar\omega_{eg}$ is the energy difference between $|e)$ and $|g)$, and $\Delta$ is the dimensionless offset of the excited state surface relative to the ground state.
The Hamiltonians are quantum harmonic oscillators.
The solutions to the harmonic oscillator Hamiltonian are well known, and their position space wavefunctions are
\begin{equation}
	\psi_m(q) = \langle q | m \rangle = N_m H_m(q) \exp(-q^2/2),
\end{equation}
where $N_m = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the $m^{th}$ Hermite Polynomial.\cite{RN230, MorseFeshbach}

For an $n$-quantum excited state vibration $| \tilde{n} \rangle$, and a $m$-quantum ground state vibration $\ket{m}$, the $k^{th}$-order vibrational coupling term is
\begin{equation}
	\begin{split}
		\mel{\tilde{n}}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \ \psi^*_n(q-\Delta) q^k \psi_m(q)\\
		&= \int_{-\infty}^\infty \mathrm{d}q \ N_n H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k N_m H_m(q) \exp(-\frac{q^2}{2}) \\
		&= N_n N_m \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ H_n(q-\Delta) q^k H_m(q) \exp(-q^2 + q\Delta).
	\end{split}\label{key}
\end{equation}
The integral corresponds to Franck-Condon factors for $k=0$ and Herzberg-Teller integrals for $k=1$.
The vibrational coupling integrals are written assuming the expansion of the dipole moment is taken about the equilibirum point of the ground state geometry ($q=0$), as is done in the main text.
Note that in the limit $\Delta \rightarrow 0$, typical harmonic oscillator selection rules are restored, as the two wells have the same vibrational Hamiltonian and thus share a subspace of orthonormal eigenstates.

\subsection{General Solution to $\langle \tilde{n} | q^k | m \rangle$}
The matrix elements of \autoref{key} can be computed numerically, but analytic forms of the integral also exist. 
Due to the polynomial nature of $H_v(q)$, the product $H_n(q-\Delta) q^k H_m(q)$ will also be a polynomial, so that the integral of \autoref{key} will be of the form
\begin{eqnarray}
	\int_{-\infty}^\infty \mathrm{d}q \ P_{nmk}(q) \exp(-q^2 + q\Delta), \\
	P_{nmk}(q) \equiv \sum_\lambda^{n+m+k} a_\lambda q^\lambda
\end{eqnarray}
for some set coefficients $a_\lambda$, to be specified later. 
We can recast the integral into the linear combination of integrals,
\begin{equation}\label{eq:analytic_form}
	\mel{\tilde{n}}{q^k}{m} = N_n N_m \exp(-\frac{\Delta^2}{2}) \sum_\lambda a_\lambda F_\lambda(\Delta),
\end{equation}
where
\begin{equation}\label{integral}
	F_w(\Delta) \equiv \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta).
\end{equation}
\autoref{integral} can be readily evaluated, as we now show. 
 When $w=0$, the integral is evaluated by completing the square:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
\begin{equation}
	\begin{split}
		F_0(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 - q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
		&= \exp(\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
	\end{split}
\end{equation}
For the general solution, \autoref{integral} is evaluated via repeated use of a well-known Gaussian identity
\begin{equation}\label{identity}
	\begin{split}
		F_w(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta) = \partial_{\Delta} \int_{-\infty}^\infty \mathrm{d}q \ q^{w-1} \exp(-q^2 + q\Delta) \\
		&= \frac{\mathrm{d}}{\mathrm{d}\Delta} F_{w-1}(\Delta)
	\end{split}
\end{equation}
so we can write\footnote{Setting $-x^2 \ = \ \Delta^2/4$ (so that $x \ = \ i \Delta /2$) and using the chain rule ($\frac{\mathrm{d}}{\mathrm{d}x} =  \frac{\mathrm{d}}{\mathrm{d}\Delta}  \frac{\mathrm{d\Delta}}{\mathrm{d}x}$) provides the final result in \autoref{eq:F_solved}.}
\begin{equation}\label{eq:F_solved}
	\begin{split}
		F_w(\Delta) &= \frac{\mathrm{d}^w}{\mathrm{d}\Delta^w} F_0(\Delta) \\
		&= \sqrt{\pi} \frac{\mathrm{d}^w}{\mathrm{d}\Delta^w} \exp(\frac{\Delta^2}{4}) \\
		&= \sqrt{\pi} \left( -\frac{i}{2} \right)^w \exp(\frac{\Delta^2}{4}) H_w\left(i\frac{\Delta}{2}\right).
	\end{split}
\end{equation}
In the last line we have used the generator definition of Hermite polynomials:  $H_n(x) \equiv (-1)^n e^{x^2} \frac{\mathrm{d}^n}{\mathrm{d}x^n} e^{-x^2}$.\cite{MorseFeshbach}

@@

It is clear from \autoref{fig:fcht_product} that the HDFG spectrum will have a significant dependence upon $\Delta$, even for small deviations from complete overlap. 
To this end, we plot the impact of offset ($\Delta$), vibrational frequency ($\omega_{g1,g0}$), and linewidth ($\Gamma$) on the HDFG spectrum \autoref{fig:chgdelta}, using values reported by Myers et al. and Brennan et al (\autoref{fig:chgdelta}). \cite{Myers1982, Brennan2024}
We maintain the relationship $\max \left(\abs{B}/\abs{A}\right) \sim$ 0.1 at $\Delta = 0.5$ to facilitate comparison to the results in the main text.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/changedelta.png}
	\caption{The impact of offset, vibrational resonance, and linewidth on HDFG spectra. Parameters for (a,b) follow from Myers et al., whereas parameters for (c,d) follow from Brennan et al.\cite{Myers1982, Brennan2024}
} 
	\label{fig:chgdelta}
\end{figure}

In addition to the linewidth and offset impacting the shape of the HDFG response, the sign of the molecular parameters $M^{ge}_0, \Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q}$ will significantly impact the HDFG spectrum.
As discussed in the main text, the atypical lineshape in the post-resonance region of the HDFG region arises due to the sign of all four aforementioned parameters being identical.
Changing the sign of one (or three) parameters will change the sign of $A, B$ and eliminate interference between the real and imaginary terms.  
As an example, we demonstrate the resultant HDFG spectrum when $M_0^{ge} < 0$, and all other terms $>0$ (\autoref{fig:chgsign}).
Compared to Figure 3 of the main text, the contributions from the $A, B_1$ and $B_2$ terms to $\Re(\gamma)$ and $\Im(\gamma)$ significantly change.
In particular, $\Re(\gamma)$ and $\Im(\gamma)$ are of similar value in the post-resonance region, eliminating the interference seen in Figure 3 of the main text.
\newpage
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/drsive_chgsign.png}
	\caption{Contributions of $A, B$ to HDFG spectrum for a simple two harmonic well system, identical to the main text, except $M^{ge}(q) = M^{ge}_0 \left(-1 + 0.04 q + \order{q^2}\right)$.
		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c, d) real and imaginary parts of terms plotted in (b), respectively.
		The spectra are scaled to $\max{(A+B)}$. 
		The vibronic one and two photon absorption operators are scaled such that $\max(\abs{B}/\abs{A}) \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
} 
	\label{fig:chgsign}
\end{figure}
\pagebreak
\section{Evaluating impact of static inhomogeneity on HDFG output}
In this section, the integral
\begin{equation}\label{generalcontour}
	\begin{split}
		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
		&= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)} \\
		&= \frac{\eta_{ijkl} \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + c\xi}\\
	\end{split}
\end{equation}
is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) and $c=1$ (electronic state and vibrational state energy fluctuations are correlated).

Integrals such as \autoref{generalcontour} can be evaluated by using the Residue theorem.\cite{MorseFeshbach}
For clarity, we briefly outline the technique.
Consider the integral
\begin{equation}
	\int_{-\infty}^{\infty} \mathrm{d}x f(x)
\end{equation}
If $\int_{-\infty}^{\infty} \mathrm{d}x f(x)$ exists %is this strict enough?
and $f(z)$ is analytic, where $z$ is a complex variable, then
\begin{subequations}\label{eq:generalcontour}
	\begin{equation}
		\int_{-\infty}^{\infty}  \mathrm{d}x f(x) = 2\pi i \sum_k \Res[f(z_k)]
	\end{equation}
where $\Res[f(z_k)]$ refers to the residue of $f(z)$ in the upper half of the complex plane at the pole $z_k$ and the sum is taken over all the poles, i.e., non-removable singularities, of $f(z)$.
Note that the residue of an n$^{\text{th}}$ order pole at $z = z_k$ is evaluated as
	\begin{equation}
		\Res[f(z_k)] = \lim_{z \rightarrow z_k} \frac{1}{\left(n-1\right)!} \frac{\mathrm{d}^{n-1}}{\mathrm{d}z^{n-1}} \left[f(z) (z-z_k)^n \right]
	\end{equation}
For first order poles (the cases considered below), $n=1$, so that 
	\begin{equation}
		\int_{-\infty}^{\infty} \mathrm{d}x f(x) = 2\pi i \sum_k \lim_{z \rightarrow z_k} f(z) (z-z_k)
	\end{equation}
\end{subequations}
Note that in \autoref{eq:generalcontour}, the integrals are evaluated along a contour which wraps all the poles in the positive half of the complex plane.

\subsection{Anti-correlated Modes}
For anti-correlated modes ($c = -1$), the poles ($\xi_k$) are situated in the complex plane as shown in \autoref{fig:contours}a.
For c = -1, there are four poles: $\pm i \sigma, \Delta_{ga}, \Delta_{ba}$. 
The contour that envelops the upper half of the complex plane has only one pole, $i \sigma$.
Using the residue theorem for a first order pole,\cite{Carlson1990line} we see
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{z \rightarrow z_k} P(z) \gamma_{ijkl}(z) (z - z_k)\\
			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{z \rightarrow i\sigma} \frac{1}{(z + i\sigma)(z- i\sigma)} \frac{1}{\Delta_{ga} - z} \frac{1}{\Delta_{ba} - z} (z - i \sigma)\\
			&= 2 \eta_{ijkl} \sigma i \lim_{z \rightarrow i\sigma} \frac{1}{z + i\sigma} \frac{1}{\Delta_{ga} - z} \frac{1}{\Delta_{ba} - z}\\
			&= 2\eta_{ijkl} \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} - i\sigma}\\
			&= \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma\right)\left(\Delta_{ba}-i \sigma\right)}\\
		\end{split}
	\end{equation}
\end{widetext}

\subsection{Correlated Modes}
For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
We evaluate along the contour that encloses the poles $\{i\sigma, -\Delta_{ba}\}$.
Since $i\sigma \neq -\Delta_{ba}$, i.e., the poles are nondegenerate, we have two first order poles, giving
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{z \rightarrow z_k} P(z) \gamma_{ijkl}(z) (z - z_k)\\
			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi}  \lim_{z \rightarrow i\sigma} \frac{1}{(z + i\sigma)(z - i\sigma)} \frac{1}{\Delta_{ga} - z} \frac{1}{\Delta_{ba} + z} \left(z - i \sigma\right) \\ 
			&+ 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{z \rightarrow -\Delta_{ba}} \frac{1}{(z + i\sigma)(z - i\sigma)} \frac{1}{\Delta_{ga} - z} \frac{1}{\Delta_{ba} + z} \left(z + \Delta_{ba}\right)\\
			&= 2 \eta_{ijkl} i \sigma \left(\frac{1}{2 i \sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} + i\sigma} \right) + 2\eta_{ijkl} i \sigma \left(\frac{1}{\sigma^2 + \Delta_{ba} ^2} \frac{1}{\Delta_{ga} + \Delta_{ba}} \right)\\
			&= \frac{\eta_{ijkl}}{\Delta_{ba} + i \sigma} \left(\frac{1}{\Delta_{ga} - i \sigma} + \frac{2i\sigma}{(\Delta_{ba} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right)\\
		\end{split}
	\end{equation}
\end{widetext}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/contour.png}
	\caption{Poles (blue dots) and contours (black lines) used to evaluate \autoref{generalcontour} for (a) anti-correlated ($c=-1$) and (b) correlated ($c=1$) modes. 
	} 
	\label{fig:contours}
\end{figure}
